Global Value Chain Analysis of LMICs

### 2016-05-19 Draft.tex
updated draft

In this section we look into stylised facts on GVC integration that are typically based on smaller samples with our extensive OECD ICIO dataset. We start by examining the development of the most basic measure of GVC integration introduced by \citet{dahuetal01}, namely the amount of foreign value added in exports labeled by \citet{ribajalo13} as $i2e$.\footnote{Note that at the aggregate level forward and backward linkages are identical and thus we only look at one of the two measures.} It captures backward linkages into value chains and shows the well-known increase in GVC integration from 1995 to 2011. As illustrated in Figure \ref{fig:i2e_t}, the value of $i2e$ has grown by approximately 350\% and by 35\% as a share of total exports from around 17\% to over 23\%. Thus, countries rely for their export production increasingly on inputs produced abroad. The numbers are in line with similar findings by \citet{rojoguno12b} but their sample ends in 2009. It is then interesting to see that after the slump during the financial crises in 2009, GVCs have quickly recovered and already have started to exceed their pre-crisis levels in 2011.

\begin{figure}
\centering
\label{fig:i2e_t}
\includegraphics[scale=0.4]{i2epercentage.png}
\caption{The development of GVC integration over time}
\end{figure}

@@

%pdc change over time figure

@@

% sectoral graph i2e

@@

With respect to services, it is also indicative of the servicification of manufacturing as described by \citet{ribaetal15}. This means that an increasing share of manufacturing gross exports is actually value added generated in services sectors and then embedded in the intermediate exports of manufacturers. This importance of services sectors for exports cannot be seen from standard gross trade statistics and thus constitutes a major advantage of trade in value added measures. It is also indicative of a growing internationalisation of services. Increasingly, services are being offshored and sourced from abroad. In that respect, it is also interesting to note that despite the low absolute $i2e$ shares, it is in services where a lot of the growth in $i2e$ has taken place. As can be seen in Figure \ref{fig:i2e_st}, five out of the six sectors with the highest growth in $i2e$ shares are services sectors.

% sectoral graph e2r

@@

%country graph i2e

@@

%country graph e2r

>>>>

In this section we look with our extensive OECD ICIO dataset into stylised facts on GVC integration that are typically based on smaller samples. We start by examining the development of the most basic measure of GVC integration introduced by \citet{dahuetal01}, namely the amount of foreign value added in exports labeled by \citet{ribajalo13} as $i2e$.\footnote{Note that at the aggregate level forward and backward linkages are identical and thus we only look at one of the two measures.} It captures backward linkages into value chains and shows the well-known increase in GVC integration from 1995 to 2011. As illustrated in Figure \ref{fig:i2e_t}, the value of $i2e$ has grown by approximately 350\% and by 35\% as a share of total exports from around 17\% to over 23\%. Thus, countries rely for their export production increasingly on inputs produced abroad. The numbers are in line with similar findings by \citet{rojoguno12b} but their sample ends in 2009. It is then interesting to see that after the slump during the financial crises in 2009, GVCs have quickly recovered and already have started to exceed their pre-crisis levels in 2011.

%\begin{figure}[h]
%\centering
%\label{fig:i2e_t}
%\includegraphics[width=7cm]{i2epercentage.png}
%\caption{The development of GVC integration over time}
%\end{figure}

@@

\begin{figure}
\centering
\begin{minipage}{0.45\textwidth}
\vspace{0.8cm}
\centering
\includegraphics[width=\textwidth]{i2epercentage.png}
\caption{The development of GVC integration over time}
\label{fig:i2e_t}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{pdcII.png}
\caption{The development of double counted trade over time}
\label{fig:pdc_t}
\end{minipage}
\end{figure}

@@

\begin{figure}
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{industries_i2e_top6.png}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{industries_i2e_bottom6.png}
\end{minipage}
\caption{Sectoral backward linkages into GVCs - Top and bottom 6.}
\label{fig:i2e_s}
\end{figure}

@@

With respect to services, it is also indicative of the servicification of manufacturing as described by \citet{ribaetal15}. This means that an increasing share of manufacturing gross exports is actually value added generated in services sectors and then embedded in the intermediate exports of manufacturers. This importance of services sectors for exports cannot be seen from standard gross trade statistics and thus constitutes a major advantage of trade in value added measures. It is also indicative of a growing internationalisation of services. Increasingly, services are being offshored and sourced from abroad. In that respect, it is also interesting to note that despite the low absolute $i2e$ shares, it is in services where a lot of the growth in $i2e$ has taken place. Five out of the six sectors with the highest growth in $i2e$ shares are services sectors.

\begin{figure}
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{industries_e2r_top6.png}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{industries_e2r_bottom6.png}
\end{minipage}
\caption{Sectoral forward linkages into GVCs - Top and bottom 6.}
\label{fig:e2r_s}
\end{figure}

@@

\begin{figure}
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{country_i2e_top_6.png}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{countries_i2e_bottom_6.png}
\end{minipage}
\caption{Countries' backward linkages into GVCs - Top and bottom 6.}
\label{fig:i2e_k}
\end{figure}

@@

\begin{figure}
\centering
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{country_e2r_top_6.png}
\end{minipage}\hfill
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{countries_e2r_bottom_6.png}
\end{minipage}
\caption{Countries' forward linkages into GVCs - Top and bottom 6.}
\label{fig:e2r_k}
\end{figure}
